---
title: "CCC Fall 2021 Student Survey"
author: "Mia"
output: pdf_document
---
### Clear Global Environment
```{r, include = TRUE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
rm(list=ls())
```

### Working Directory and Loading Packages
```{r, message = FALSE,echo = TRUE}
# Setting the Working Directory
setwd("~/Desktop/CCC-IOP/Data/CCC-Survey")

# Loading Packages
library(readxl)
library(tidyverse)
library(dplyr)
library(ggplot2)
# Theme color
CCC <- "#0065A4"
```

### Load ataset
```{r}
# Read the Fall student survey data 
Fall_2021<- read_excel("Clean_Fall2021_Student.xlsx", 
                           sheet = "Raw Data")
as.matrix(colSums(is.na(Fall_2021)))
```

### User Language
```{r, warning=FALSE}
# Summarize User Language
Q0_ul <- Fall_2021 %>%
  group_by(`User Language`) %>%
  summarise(count = n(),
            percentage = count/1163)
# Plot
ggplot(data = Q0_ul,aes(x = `User Language`, y = `percentage`)) +
  geom_col(fill = CCC) +
  geom_text(aes(label=count), vjust = -0.5, face = "bold")+
  scale_y_continuous(breaks = seq(0,0.7,0.1),
                     limits = c(0,0.7))+
  labs(title = "User language Distribution",
       x = "Language Type",
       y = "Percentage") +
  theme_classic() +  
  theme(plot.title = element_text(size = 15, face = "bold", hjust = 0.5))
```

### College
```{r, warning=FALSE}
# Summarize College Data
colnames(Fall_2021)[2] <- "college" # Rename

Q1_college <- Fall_2021 %>%
  group_by(`college`) %>%
  summarise(count = n(),
            percentage = count/1163) %>%
  arrange(desc(percentage))

# Simplify the name
Q1_college$`college` <- c("Daley",
                       "Truman",
                       "Wright",
                       "Malcolm X",
                       "Olive-Harvey",
                       "Kennedy-King")

# Plot
ggplot(data = Q1_college,aes(x = reorder(`college`,-`count`), y = `percentage`)) +
  geom_col(fill = CCC) +
  geom_text(aes(label=count), vjust = -0.5, face = "bold") +
  scale_y_continuous(breaks = seq(0,0.4,0.1),
                     limits = c(0,0.4))+
  labs(title = "College Distribution",
       caption = "Q1: What College are you Attending?",
       x = "College",
       y = "Percentage") +
  theme_classic() +  
  theme(plot.title = element_text(size = 15, face = "bold", hjust = 0.5),
        axis.text = element_text(size = 10, hjust = 0.5),
        plot.caption = element_text(face = "italic",hjust = 0))
```

### Courses
```{r, warning=FALSE}
# Summarize College Data
colnames(Fall_2021)[3] <- "courses" # Rename

Q2_courses <- Fall_2021 %>%
  drop_na(`courses`) %>%
  group_by(`courses`) %>%
  summarise(count = n(),
            percentage = count/1162) %>%
  arrange(desc(percentage))
# Rename
Q2_courses$`courses` <- c("ESL",
                       "Math",
                       "Language Arts",
                       "Bridge",
                       "Computer",
                       "Test Skills",
                       "Citizenship",
                       "Career")

# Plot
ggplot(data = Q2_courses,aes(x = reorder(`courses`,-`count`), y = `percentage`)) +
  geom_col(fill = CCC) +
  geom_text(aes(label=count), vjust = -0.5, face = "bold") +
  scale_y_continuous(breaks = seq(0,0.7,0.1),
                     limits = c(0,0.7))+
  labs(title = "Course Distribution",
       caption = "Q2: What Classes are you taking?",
       x = "Course",
       y = "Percentage") +
  theme_classic() +  
  theme(plot.title = element_text(size = 15, face = "bold", hjust = 0.5),
        axis.text = element_text(size = 10, hjust = 0.5),
        plot.caption = element_text(face = "italic",hjust = 0))
```

### Teaching Modality
```{r}
# Summarize Teaching Nodality Data
colnames(Fall_2021)[4] <- "format" # Rename


Q3_format <- Fall_2021 %>%
  drop_na(`format`) %>%
  group_by(`format`) %>%
  summarise(count = n(),
            percentage = count/(1163-8)) %>%
  arrange(desc(percentage))
# Rename
Q3_format$`format` <- c("online",
                        "in person")

# Plot
ggplot(data = Q3_format,aes(x = reorder(`format`,-`count`), y = `percentage`)) +
  geom_col(fill = CCC) +
  geom_text(aes(label=count), vjust = -0.5, face = "bold") +
  scale_y_continuous(breaks = seq(0,0.8,0.1),
                     limits = c(0,0.8))+
  labs(title = "Teaching Modality",
       caption = "Q3: Is this class on campus(in person)?",
       x = "Format",
       y = "Percentage") +
  theme_classic() +  
  theme(plot.title = element_text(size = 15, face = "bold", hjust = 0.5),
        axis.text = element_text(size = 10, hjust = 0.5),
        plot.caption = element_text(face = "italic",hjust = 0))
```

### Instruction Difficulty Level
```{r}
# Summarize Teaching foramt Data
colnames(Fall_2021)[5] <- "difficulty" # Rename


Q4_difflev <- Fall_2021 %>%
  drop_na(`difficulty`) %>%
  group_by(`difficulty`) %>%
  summarise(count = n(),
            percentage = count/(1163-2)) %>%
  arrange(desc(percentage))

# Plot
ggplot(data = Q4_difflev,aes(x = reorder(`difficulty`,-`count`), y = `percentage`)) +
  geom_col(fill = CCC) +
  geom_text(aes(label=count), vjust = -0.5, face = "bold") +
  scale_y_continuous(breaks = seq(0,0.9,0.1),
                     limits = c(0,0.9))+
  labs(title = "Instruction Difficulty Level",
       caption = "Q4: Instruction is at the right level for me in this class",
       x = "Instruction difficulty level",
       y = "Percentage") +
  theme_classic() +  
  theme(plot.title = element_text(size = 15, face = "bold", hjust = 0.5),
        axis.text = element_text(size = 10, hjust = 0.5),
        plot.caption = element_text(face = "italic",hjust = 0))
```

### Instruction Pace
```{r}
# Summarize Teaching foramt Data
colnames(Fall_2021)[6] <- "pace" # Rename


Q5_pace <- Fall_2021 %>%
  drop_na(`pace`) %>%
  group_by(`pace`) %>%
  summarise(count = n(),
            percentage = count/(1163-2)) %>%
  arrange(desc(percentage))

# Plot
ggplot(data = Q5_pace ,aes(x = reorder(`pace`,-`count`), y = `percentage`)) +
  geom_col(fill = CCC) +
  geom_text(aes(label=count), vjust = -0.5, face = "bold") +
  scale_y_continuous(breaks = seq(0,0.9,0.1),
                     limits = c(0,0.9))+
  labs(title = "Instruction Pace",
       caption = "Q5: The pace of this class is okay for me",
       x = "Instruction Pace",
       y = "Percentage") +
  theme_classic() +  
  theme(plot.title = element_text(size = 15, face = "bold", hjust = 0.5),
        axis.text = element_text(size = 10, hjust = 0.5),
        plot.caption = element_text(face = "italic",hjust = 0))
```


### Help from Teachers
```{r}
# Clean data
colnames(Fall_2021)[7] <- "thelp" # Rename
Q6_thelp <- Fall_2021 %>%
  drop_na(`thelp`)

Q6_thelp <- Q6_thelp %>%
  separate_rows(thelp, sep = ",") %>% # separate multiple choices by individual
  group_by(thelp) %>%
  summarise(count = n(),
            percentage = count/(1163-1)) %>%
  arrange(desc(percentage))
Q6_thelp
```

### Other Help from Teachers
```{r}
# Summarize Teaching format Data
colnames(Fall_2021)[8] <- "othelp" # Rename
```

### Welcome from Teachers
```{r}
# Summarize Data
colnames(Fall_2021)[9] <- "welcome" # Rename

Q8_welcome <- Fall_2021 %>%
  drop_na(`welcome`) %>%
  group_by(`welcome`) %>%
  summarise(count = n(),
            percentage = count/(1163-1)) %>%
  arrange(desc(percentage))

# Plot
ggplot(data = Q8_welcome,aes(x = reorder(`welcome`,-`count`), y = `percentage`)) +
  geom_col(fill = CCC) +
  geom_text(aes(label=count), vjust = -0.5, face = "bold") +
  scale_y_continuous(breaks = seq(0,1,0.1),
                     limits = c(0,1))+
  labs(title = "Welcome Level from Teachers",
       caption = "Q8: The teacher helps me to feel welcome in this class",
       x = "Welcome level",
       y = "Percentage") +
  theme_classic() +  
  theme(plot.title = element_text(size = 15, face = "bold", hjust = 0.5),
        axis.text = element_text(size = 10, hjust = 0.5),
        plot.caption = element_text(face = "italic",hjust = 0))
```

### Respect from Teachers
```{r}
# Summarize Data
colnames(Fall_2021)[10] <- "respect" # Rename

Q9_respect <- Fall_2021 %>%
  drop_na(`respect`) %>%
  group_by(`respect`) %>%
  summarise(count = n(),
            percentage = count/(1163-2)) %>%
  arrange(desc(percentage))

# Plot
ggplot(data = Q9_respect,aes(x = reorder(`respect`,-`count`), y = `percentage`)) +
  geom_col(fill = CCC) +
  geom_text(aes(label=count), vjust = -0.5, face = "bold") +
  scale_y_continuous(breaks = seq(0,1,0.1),
                     limits = c(0,1))+
  labs(title = "Respect Level from Teachers",
       caption = "Q9: The teacher of this class speaks to all students with respect.",
       x = "Welcome level",
       y = "Percentage") +
  theme_classic() +  
  theme(plot.title = element_text(size = 15, face = "bold", hjust = 0.5),
        axis.text = element_text(size = 10, hjust = 0.5),
        plot.caption = element_text(face = "italic",hjust = 0))
```

### Student Support Services Noted by Teachers
```{r}
# Summarize Data
colnames(Fall_2021)[11] <- "suppsv" # Rename

Q12_suppsv <- Fall_2021 %>%
  drop_na(`suppsv`) %>%
  group_by(`suppsv`) %>%
  summarise(count = n(),
            percentage = count/(1163-2)) %>%
  arrange(desc(percentage))

# Plot
ggplot(data = Q12_suppsv,aes(x = reorder(`suppsv`,-`count`), y = `percentage`)) +
  geom_col(fill = CCC) +
  geom_text(aes(label=count), vjust = -0.5, face = "bold") +
  scale_y_continuous(breaks = seq(0,1,0.1),
                     limits = c(0,0.8))+
  labs(title = "Information of Student Support Services given by Teachers",
       caption = "Q12: My teacher has given me information about student support services, such as tutoring, the wellness center, academic advising, and career planning.",
       x = "Support service ",
       y = "Percentage") +
  theme_classic() +  
  theme(plot.title = element_text(size = 15, face = "bold", hjust = 0.5),
        axis.text = element_text(size = 10, hjust = 0.5),
        plot.caption = element_text(face = "italic",hjust = 0))
```

### Book Difficulty Level
```{r}
# Summarize Data
colnames(Fall_2021)[12] <- "bookdiff" # Rename

Q10_bookdiff <- Fall_2021 %>%
  drop_na(`bookdiff`) %>%
  group_by(`bookdiff`) %>%
  summarise(count = n(),
            percentage = count/(1163-1)) %>%
  arrange(desc(percentage))

# Plot
ggplot(data = Q10_bookdiff, aes(x = reorder(`bookdiff`,-`count`), y = `percentage`)) +
  geom_col(fill = CCC) +
  geom_text(aes(label=count), vjust = -0.5, face = "bold") +
  scale_y_continuous(breaks = seq(0,1,0.1),
                     limits = c(0,1))+
  labs(title = "Book Difficulty Level Fitness",
       caption = "Q10: The books and materials for this class are at the right level for me.",
       x = "Book Difficulty Level ",
       y = "Percentage") +
  theme_classic() +  
  theme(plot.title = element_text(size = 15, face = "bold", hjust = 0.5),
        axis.text = element_text(size = 10, hjust = 0.5),
        plot.caption = element_text(face = "italic",hjust = 0))
```

### Access to Course Materials
```{r}
# Summarize Data
colnames(Fall_2021)[13] <- "access" # Rename

Q11_access <- Fall_2021 %>%
  drop_na(`access`) %>%
  group_by(`access`) %>%
  summarise(count = n(),
            percentage = count/(1163-3)) %>%
  arrange(desc(percentage))

# Plot
ggplot(data = Q11_access, aes(x = reorder(`access`,-`count`), y = `percentage`)) +
  geom_col(fill = CCC) +
  geom_text(aes(label=count), vjust = -0.5, face = "bold") +
  scale_y_continuous(breaks = seq(0,0.9,0.1),
                     limits = c(0,0.9))+
  labs(title = "Access to Books and Materials Needed for Classes",
       caption = "Q11. I have access to the books and materials I need for this class.",
       x = "Access to course material ",
       y = "Percentage") +
  theme_classic() +  
  theme(plot.title = element_text(size = 15, face = "bold", hjust = 0.5),
        axis.text = element_text(size = 10, hjust = 0.5),
        plot.caption = element_text(face = "italic",hjust = 0))
```  

### Recommending CCC Courses
```{r}
# Summarize Data
colnames(Fall_2021)[14] <- "recommendation" # Rename

Q13_recommendation <- Fall_2021 %>%
  drop_na(`recommendation`) %>%
  group_by(`recommendation`) %>%
  summarise(count = n(),
            percentage = count/(1163-1)) %>%
  arrange(desc(percentage))

# Plot
ggplot(data = Q13_recommendation, aes(x = reorder(`recommendation`,-`count`), y = `percentage`)) +
  geom_col(fill = CCC) +
  geom_text(aes(label=count), vjust = -0.5, face = "bold") +
  scale_y_continuous(breaks = seq(0,1,0.1),
                     limits = c(0,1))+
  labs(title = "Recommendation of CCC Courses to Friends",
       caption = "Q13: I would recommend this class to a friend",
       x = "Recommendation to Friends",
       y = "Percentage") +
  theme_classic() +  
  theme(plot.title = element_text(size = 15, face = "bold", hjust = 0.5),
        axis.text = element_text(size = 10, hjust = 0.5),
        plot.caption = element_text(face = "italic",hjust = 0))
```

### Reasons of Not Recommending CCC Courses
```{r}
# Summarize Data
colnames(Fall_2021)[15] <- "norecommend" # Rename
Q13b_norecommend <- Fall_2021 %>%
  drop_na(norecommend)
table(Q13b_norecommend$norecommend)
```

### Analysis of students who do not recommend CCC Coruses
```{r}
Q13b_norecommend <- Fall_2021 %>%
  filter(recommendation == "no")
as.matrix(colSums(is.na(Q13b_norecommend)))
# User Language
Q13b_norecommend %>%
  group_by(`User Language`) %>%
  summarise(count = n(),
            percentage = count/57)
# College
Q13b_norecommend %>%
  group_by(`college`) %>%
  summarise(count = n(),
            percentage = count/57) %>%
  arrange(desc(percentage))
# Courses
Q13b_norecommend %>%
  drop_na(`courses`) %>%
  group_by(`courses`) %>%
  summarise(count = n(),
            percentage = count/57) %>%
  arrange(desc(percentage))
# Format
Q13b_norecommend %>%
  drop_na(`format`) %>%
  group_by(`format`) %>%
  summarise(count = n(),
            percentage = count/54) %>%
  arrange(desc(percentage))
# Respect
Q13b_norecommend %>%
  drop_na(`respect`) %>%
  group_by(`respect`) %>%
  summarise(count = n(),
            percentage = count/56) %>%
  arrange(desc(percentage))
```

#### Significant Differences Compared to Students Recommending CCC Courses
```{r}
# Difficulty
Q13b_norecommend %>%
  drop_na(`difficulty`) %>%
  group_by(`difficulty`) %>%
  summarise(count = n(),
            percentage = count/56) %>%
  arrange(desc(percentage))
# Pace
Q13b_norecommend %>%
  drop_na(`pace`) %>%
  group_by(`pace`) %>%
  summarise(count = n(),
            percentage = count/56) %>%
  arrange(desc(percentage))
# Help from teachers
Q13b_norecommend %>%
  drop_na(`thelp`) %>%
  separate_rows(thelp, sep = ",") %>% 
  group_by(`thelp`) %>%
  summarise(count = n(), # Much lower rate of making class interesting
            percentage = count/56) %>% # Lower rate of test-taking skills
  arrange(desc(percentage))
# Welcome
Q13b_norecommend %>%
  drop_na(`welcome`) %>%
  group_by(`welcome`) %>%
  summarise(count = n(),
            percentage = count/56) %>%
  arrange(desc(percentage))
# Support Service
Q13b_norecommend %>%
  drop_na(`suppsv`) %>%
  group_by(`suppsv`) %>%
  summarise(count = n(),
            percentage = count/56) %>%
  arrange(desc(percentage))
# Book Level
Q13b_norecommend %>%
  drop_na(`bookdiff`) %>%
  group_by(`bookdiff`) %>%
  summarise(count = n(),
            percentage = count/56) %>%
  arrange(desc(percentage))
# Access
Q13b_norecommend %>%
  drop_na(`access`) %>%
  group_by(`access`) %>%
  summarise(count = n(),
            percentage = count/55) %>%
  arrange(desc(percentage))
```