---
title: "CCC Spring 2021 Student Survey"
author: "Mia"
date: "4/6/2022"
output: pdf_document
---

### Clear Global Environment
```{r, include = TRUE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
```

### Working Directory and Loading Packages
```{r, message = FALSE,echo = TRUE}
# Setting the Working Directory
setwd("~/Desktop/CCC-IOP/Data/S")

# Loading Packages
library(readxl)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(tidytext)
```

## Q2.a
### Load ataset
```{r, warning=FALSE}
# Read the FiW data 
Spring_2021<-read_excel("Clean_Spring2021_Student.xlsx", 
                          sheet = "Raw Data")
```

### Classes
```{r, warning=FALSE}
# Rename
colnames(Spring_2021)[3] <- "Courses" 

# Check NA values
summary(is.na(Spring_2021$Courses))
table(Classes$Courses)
# Create dataset of Course Information
Classes <- Spring_2021 %>%
  unnest_tokens(Courses,Courses) %>%
  drop_na(`Courses`) %>% # Remove NA values
  filter(Courses %in% c("math","arts", "esl","computer","social","bridge","science", "ged")) %>%
  group_by(`Courses`) %>% # group by courses
  summarise(count = n(),
            percentage = count/(767-5))
glimpse(Classes)

# Format course name to align with Fall survey
Classes$Courses <- c("Language Arts", 
                     "Bridge", 
                     "Computer Skills",
                     "ESl",
                     "GED",
                     "Math",
                     "Science",
                     "Social Studies")

# Plot
ggplot(data = Classes, aes(x = reorder(`Courses`,-`count`), y = `percentage`)) +
  geom_col(fill = "maroon") +
  geom_text(aes(label=count), vjust = -0.5, face = "bold")+
  labs(title = "Course Distribution",
       x = "Course Type",
       y = "Percentage") +
  theme_classic() +  
  theme(plot.title = element_text(size = 15, face = "bold", hjust = 0.5))
```
### College
```{r, warning=FALSE}
# Summarize College Data
colnames(Fall_2021)[2] <- "College" # Rename

College <- Fall_2021 %>%
  group_by(`College`) %>%
  summarise(count = n(),
            percentage = count/1163) %>%
  arrange(desc(percentage))

# Simplify the name
College$`College` <- c("Daley",
                       "Truman",
                       "Wright",
                       "Malcolm X",
                       "Olive-Harvey",
                       "Kennedy-King")

# Plot
ggplot(data = College,aes(x = reorder(`College`,-`count`), y = `percentage`)) +
  geom_col(fill = "maroon") +
  geom_text(aes(label=count), vjust = -0.5, face = "bold") +
  scale_y_continuous(breaks = seq(0,0.4,0.1),
                     limits = c(0,0.4))+
  labs(title = "College Distribution",
       caption = "Q1: What College are you Attending?",
       x = "College",
       y = "Percentage") +
  theme_classic() +  
  theme(plot.title = element_text(size = 15, face = "bold", hjust = 0.5),
        axis.text = element_text(size = 10, hjust = 0.5),
        plot.caption = element_text(face = "italic",hjust = 0))
```


# Clean dataset
FiW_his_por <- FiW_his_por %>%
  drop_na(Year_ori) %>% # Delete NA Value
  select(-starts_with("..."), -starts_with("Number"),#Delete irrelevant columns
         -"FIW Survey Edition*" , -"Total Countries") 


# Add formatted value between 2003 to 2006 to original dataset
q1_FiW_his_por <- rbind(FiW_his_por, d2006, d2005,d2004,d2003) %>% 
  mutate(Year = as.numeric(Year_ori)) %>% 
  # Create a new column to convert values of Year into numeric
  select(-"Year_ori") %>% # Delete the column with Year information in character
  filter(Year >= 1995 & Year <= 2020) %>% # Only keep values from 1995 to 2020
  arrange(Year) %>% # Arrange the year column in ascending order
  select(Year,everything()) # Move the year column to the first in the dataframe

# Summarize the distribution in 1995 and 2020
q1_FiW_his_por %>%
  filter(Year == 1995 | Year == 2020) %>% # Only keeps YEar 1995 and 2020
  group_by(Year) %>% # Group based on year
  summarize(Free = sum(`% of F Countries`), # summarize percentage of each type 
            Partially_Free = sum(`% of PF Countries`),
            Non_Free = sum(`% of NF Countries`)) +
```

### Plot the historical distribution
```{r}
plot_q1 <- q1_FiW_his_por %>%
  ggplot() +
  geom_line(mapping = aes(x=Year, y= `% of F Countries`, color = "% of F Countries"),
            size = 0.7) +
  geom_point(aes(x = 2020, y = 0.4205128, color = "% of F Countries"), size = 2) +
  geom_line(mapping = aes(x=Year, y= `% of PF Countries`, color = "% of PF Countries"), 
            size = 0.7) + 
  geom_point(aes(x = 2020, y = 0.3025641, color = "% of PF Countries"), size = 2) + 
  geom_line(mapping = aes(x=Year, y= `% of NF Countries`, color = "% of NF Countries"),
            size = 0.7) +
  geom_point(aes(x = 2020, y = 0.2769231, color = "% of NF Countries"), size = 2) +
  scale_x_continuous(breaks = c(1995,2000,2005,2010,2015,2020),
                     limits = c(1993,2022)) +
  scale_y_continuous(breaks = c(0.2,0.3,0.4,0.5),
                     limits = c(0.2,0.5))+
  labs(title = "Distribution of Freedom in the World",
       subtitle = "Year 1995 to 2020", caption = 
      "Source: Freedom House.(2021).Country and Territory Ratings and Statues, 1973-2021",
    x = "Year",
    y = "Share of Global Distribution") +
  scale_color_brewer(
    name = "Freedom Status",
    labels = c("Free", "Not Free", "Partially Free"),
    palette= "Dark2") +
  theme_light() +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.caption = element_text(face = "italic", hjust = 0),
        panel.grid.minor = element_blank()
  )  
plot_q1 +
  annotate(geom = "label", x = 1995, y = 0.385,
  label = "0.3979", color = "#1B9E77", fill = NA,fontface = "bold", label.size = NA) +
  annotate(geom = "label", x = 1995, y = 0.338,
  label = "0.3246", color = "#7570B3", fill = NA, fontface = "bold", label.size = NA) +
  annotate(geom = "label", x = 1995, y = 0.262,
  label = "0.2775", color = "#D95F02", fill = NA,fontface = "bold", label.size = NA) +
  annotate(geom = "label", x = 2020.2, y = 0.405,
  label = "0.4205", color = "#1B9E77", fill = NA,fontface = "bold", label.size = NA) +
  annotate(geom = "label", x = 2021, y = 0.326,
  label = "0.3026", color = "#7570B3", fill = NA,fontface = "bold", label.size = NA) +
  annotate(geom = "label", x = 2021, y = 0.257,
  label = "0.2769", color = "#D95F02", fill = NA, fontface = "bold", label.size = NA) 
```
\newpage

## Q2.b

### Read by country dataset
```{r, warning=FALSE}
# Read the by country FiW data 
FiW_cty <- read_excel("Qb_Country Rating, Statuses_Clean.xlsx")
# Changes made to the original dataset:
# 1. Only keeps information from 1995 to 2020
# 2. Delete the first row "Survey Editions",
# 3. Unmerge row " Year(s) Under Review", Delete all Status column, 
# add year information to each index being evaluated instead (both PR and CL)
str(FiW_cty)
```

### Cleaning data to get FiW Index
```{r, warning=FALSE}
# Convert each column to numeric form except the country column
FiW_cty <- FiW_cty %>%
  mutate_at(c(2:53),as.numeric)

# Create new columns to calculate the average of PR and CL for each country in each year
# Use Rollmean to calculate moving average of the adjacent two columns for each row
FiW_av <- data.frame(t(apply(FiW_cty[, c(2:53)],# start from the 2nd column,i.e.Year 1995
                             1, rollmean, 2))) 
# Finalize the average FiW value for each country-year data
FiW_av <- FiW_av[, c(TRUE,FALSE)] 
# Filter Even columns since those columns calculate the mean of 
# CL of previous year and PR of this year

# Combine the each country-year FiW value data into the original dataset and Clean
FiW_cty<-cbind(FiW_cty, FiW_av)%>% #combine data of each country-year FiW value by column
  select(-contains("...")) %>% #Delete original value columns
  slice(-c(1)) # Delete the first row which specifies category of PR and CL

# Change column names of the country-year FiW value dataset
colnames(FiW_cty) <- c("Country",  # The first column indicates country name
  c(1995:2020)) # all the other column names indicate the year the value belongs to
str(FiW_cty) 
# Get a cleaned dataset with FiW Index of each country in each year between 1995 and 2020.
# To find the value of a specific country in a single year,searching the first column to
# find the name of the country and then looking at column name to find corresponding year
```

### Rescale the FiW Index
```{r, warning = FALSE}
# Construct re-scale Rule
# Larger number indicates more democratic country
maxs <- apply((FiW_cty)[,c(2:27)], # apply the function to every FiW Value column
              2, # Calculation Range: Column
              min, # Smaller original value indicate more democratic country
              na.rm = TRUE) # do not apply the re-scale rule to NA values
# Smaller number indicates less democratic country
mins <- apply((FiW_cty)[,c(2:27)], # apply the function to every FiW Value column
              2, # Calculation Range: Column
              max, # Greater original index indicate less democratic country
              na.rm = TRUE) # do not apply the re-scale rule to NA values
# Re-scale so that the value range from 0 to 1, and larger numbers indicate more demoratic
rescal<- as.data.frame(scale((FiW_cty)[, c(2:27)],center = mins, scale = maxs - mins))

# Compare with summary (FiW-cty) to double check the correctness of rescale code
summary(rescal) 

# Combine the re-scaled dataset with original dataset
FiW_cty <- cbind(select(FiW_cty, c(1)), # only keep the country column
                 rescal) %>% # Combine re-scaled FiW Index
  format(digits = 2) %>% # format data, only keeps 3 digits
  mutate_at(c(2:27),as.numeric) # convert the format of all Index value into numeric
```

### Create two dummy variables to represent Index change status for each country-year
```{r, warning = FALSE}
# Create a subset of FiW_cty without the only character column 'country'
FiW_num <- FiW_cty %>%
  select(-'Country')
# Calculate moving difference for each country-year
FiW_num <- as.matrix(FiW_num) # convert into matrix to use functions in package "Matrix" 
# Store the difference data in a new dataframe called diff
# Use rowDiffs to calculate differences between columns in each row
diff <- data.frame(rowDiffs(FiW_num, rows = NULL, cols = NULL, 
                 lag = 1L, # calculate i - (i-1)
                 differences = 1L, useNames = NA))
colnames(diff) <- c(1996:2020) #Replace column names with the year it belongs to
# Convert back to matrix
diff <- Reduce(cbind, diff)
# Combine with the original daset and set column names
# Keep the difference and country name column
FiW_diff<-cbind(FiW_cty, diff)[, c(1, 28:52)]
# Rename each column with the year it belongs to
colnames(FiW_diff) <- c("Country",c(1996:2020))

# Create Dummy variables to indicate index changing status

         i_2020 = ifelse(FiW_diff$`2020`>0, 1, 0),
         d_2020 = ifelse(FiW_diff$`2020`<0, 1, 0)
         )
FiW_his_status <- FiW_his_status[, c(1, 27:76)] # Only keeps the dummy variables
```

### Calculate the yearly share of FiW Index Change Status
```{r, warning = FALSE}
# CLeaning data
FiW_his_status <- as.data.frame(t(FiW_his_status)) %>% # Convert row and column
  row_to_names(row_number = 1) %>% # set the first row as column names
  mutate_at(c(1:205), as.numeric) %>% # Convert column 1 to 205 into numeric format
  mutate(perct = rowMeans(., na.rm = TRUE)) %>% # calculate mean of each row
  select(perct, everything()) %>% # Move the percentage column as the 1st column
  format(digits = 2)

# Create dataset for increasing perct
inc_pct <- FiW_his_status %>%
  select(perct)
inc_pct <- as.data.frame(t(inc_pct)) %>%
  select(-contains("d"))
colnames(inc_pct) <- c(1996:2020)
rownames(inc_pct) <- c("increasing")
inc_pct <- as.data.frame(t(inc_pct))

# Create dataset for decreasing perct
de_pct <- FiW_his_status %>%
  select(perct)
de_pct <- as.data.frame(t(de_pct)) %>%
  select(-contains("i"))
colnames(de_pct) <- c(1996:2020)
rownames(de_pct) <- c("decreasing")
de_pct <- as.data.frame(t(de_pct))

# Combine data of increasing portion and decreasing portion of each year
q2_status_por_plot <- cbind(inc_pct, de_pct) %>%
  mutate(Year = c(1996:2020)) %>%
  mutate_at(c(1:3), as.numeric)
rownames(q2_status_por_plot) <- c(1:25)
```  

### Plot the yearly share of countries experience gains or losses in FiW Index
```{r}
plot_2 <- q2_status_por_plot %>%
  ggplot() +
  geom_line(mapping = aes(x= Year, y= `increasing`, color = "increasing"),size = 0.7) +
  geom_point(aes(x = 2020, y = 0.041, color = "increasing"), size = 2) +
  geom_line(mapping = aes(x= Year, y= `decreasing`, color = "decreasing"),size = 0.7) + 
  geom_point(aes(x = 2020, y = 0.108, color = "decreasing"), size = 2) +
  scale_x_continuous(breaks = c(1995,2000,2005,2010,2015,2020),
                     limits = c(1993,2022)) +
  scale_y_continuous(breaks = c(0,0.05,0.1,0.15,0.2,0.25),
                     limits = c(0,0.25)) +
  labs(title = "Share of Freedom Index Change Status \namong Global Countries",
       sbutitle = "Year 1995 to 2020",caption =
    "Source: Freedom House.(2021).Country and Territory Ratings and Statues, 1973-2021",
    x = "Year",
    y = "Share of Countries") +
  scale_color_brewer(
    name = "Freedom Index \nChange Status",
    labels = c("Losses", "Gains"),
    palette = "Dark2") +
  theme_bw() +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.caption = element_text(face = "italic", hjust = 0),
        panel.grid.minor = element_blank()
  )  

plot_2 +
  annotate(geom = "label", x = 1996, y = 0.169,
  label = "0.162", color = "#D95F02", fill = NA,fontface = "bold", label.size = NA) +
  annotate(geom = "label", x = 2007, y = 0.025,
  label = "0.031", color = "#D95F02", fill = NA,fontface = "bold", label.size = NA) +
  annotate(geom = "label", x = 2002, y = 0.226,
  label = "0.219", color = "#D95F02", fill = NA,fontface = "bold", label.size = NA) +
  annotate(geom = "label", x = 1995, y = 0.075,
  label = "0.068",color = "#1B9E77",  fill = NA,fontface = "bold", label.size = NA) +
  annotate(geom = "label", x = 2020, y = 0.031,
  label = "0.041", color = "#D95F02", fill = NA,fontface = "bold", label.size = NA) +
  annotate(geom = "label", x = 2020, y = 0.119,
  label = "0.108", color = "#1B9E77", fill = NA, fontface = "bold", label.size = NA) 

```
\newpage

## Q2.c

### Read the Country-year FiW data
```{r}
# Import FiW dataset with each country's Freedom Status
FiW_st_0520 <- read_excel("Qc_Continent_Share_Data.xlsx", sheet = 1)

# Changes made to the original dataset:
# 1. Only keeps information in 2005 and 2020
# 2. Delete the first row "Survey Editions",
# 3. Unmerge row " Year(s) Under Review", only keeps Status column,
# change the first row name to "Country Name"

# Match country name with country code
FiW_st_0520 <- as.matrix(FiW_st_0520)
code <- as.data.frame(countrycode(FiW_st_0520[,1], 
                                  origin = 'country.name', #Originally in Name Format
                                  destination = 'un')) #change to UN M94 code
# Check uncertain country codes

# 1. For Czechoslovakia, we consider it to share the same code as Czechia in the
# file provided by UN on the website
# 2. For Kosovo, there is no country code in the UN file, therefore, we keep the 
# resultget by R, i.e. NA
# 3. For Yugoslavia, Serbia, Montenegro, since there is no value for Yugoslavia 
# in both 2005 and 2020 ,we follow the UN file and just leave it as NA. 
# Serbia and Montenegro are coded per the UN code
# 4. For Micronesia, the code given in the UN file is 583, therefore, we manually
# assign the code value in the R dataframe
# 5. For Taiwan, it's part of China and there is no code in the UN file, while 
# the political system is different, therefore, we remain leave it as NA

# Combine the code data with the original dataset
FiW_st_0520 <- cbind(FiW_st_0520, code)
colnames(FiW_st_0520) <- c("country_name","2005","2020","M49 Code")
FiW_st_0520[115,4] <- 583
```

### Combine with UN datafile by M94 Code
```{r}
# Import the UN code data
UNSD <- read_excel("Qc_UNSD — Methodology.xlsx")
# Cleaning data
UNSD <- UNSD %>%
  select(`Region Code`, `Region Name`, 
         `Country or Area`, 
         `M49 Code`, 
         `Least Developed Countries (LDC)`) %>%
  drop_na(`Region Code`)
str(UNSD)

# Combine the FiW Index Status dataset and Regional code dataset by UN
# Match each row with information in UNSD dataset according to M94 Code
Cont_0520 <- left_join(FiW_st_0520, UNSD, by = "M49 Code") 
# Remove irrelevant columns for plotting
Cont_0520 <- Cont_0520 %>%
  select(-`Country or Area`) %>%
  select(`M49 Code`, everything()) %>%
  select(`Region Code`, everything()) %>%
  drop_na(`Region Code`)

# 2005 Data
d2005c <- Cont_0520 %>%
  group_by(`Region Name`) %>%
  summarize("F" = count(`2005` == "F"),
            "PF" = count(`2005` == "PF"),
            "NF" = count(`2005` == "NF"))%>%
  melt(id.vars=c("Region Name")) %>%
  arrange(`Region Name`) %>%
  mutate_at(c(3), as.numeric)
# 2020 Data
d2020c <- Cont_0520 %>%
  group_by(`Region Name`) %>%
  summarize("F" = count(`2020` == "F"),
            "PF" = count(`2020` == "PF"),
            "NF" = count(`2020` == "NF")) %>%
  melt(id.vars=c("Region Name")) %>%
  arrange(`Region Name`) %>%
  mutate_at(c(3), as.numeric)
# sum of countries of each continent
sum <- c(rep(sum(d2005c$value[d2005c$`Region Name`== "Africa"]),3),
rep(sum(d2005c$value[d2005c$`Region Name`== "Americas"]),3),
rep(sum(d2005c$value[d2005c$`Region Name`== "Asia"]),3),
rep(sum(d2005c$value[d2005c$`Region Name`== "Europe"]),3),
rep(sum(d2005c$value[d2005c$`Region Name`== "Oceania"]),3))

# Combine dataset
d2005c <- cbind(d2005c, sum)
d2020c <- cbind(d2020c, sum)

# Combine into the final dataset
q3_cont_share <- rbind(d2005c, d2020c)
q3_cont_share <- q3_cont_share %>%
  mutate(Year = c(rep(2005,15),rep(2020,15))) # Create Year column
# The amount of country increased to 43 in Europe in 2020
q3_cont_share$sum[q3_cont_share$`Region Name`=="Europe" & q3_cont_share$Year == 2020]<-43
# The amount of country increased to 54 in Africa in 2020
q3_cont_share$sum[q3_cont_share$`Region Name`=="Africa" & q3_cont_share$Year == 2020]<-54

q3_cont_share <- q3_cont_share %>%
  mutate(pct = format((value/sum),digits = 2)) %>% # Calculate the percentage
  arrange(Year,variable,desc(pct)) %>%
  mutate(coding_order = c(c(1:5),rep(6,10),c(7:11),rep(12,10)))
```  

### Plot Distribution of Freedom Index Status by Continent
```{r,, warning = FALSE}
plot3 <- ggplot(data = q3_cont_share,aes(x= reorder(`Region Name`,+ coding_order),
                                         group = Year)) + 
  geom_bar(aes(y = value, fill= variable), position = "fill",
           stat="identity") +
  ggtitle("Distribution of Freedom Index Status by Continent",
       subtitle = "Year 2005 and Year 2020")+
  labs(caption =
  "Source: Freedom House.(2021).Country and Territory Ratings and Statues, 1973-2021.
Standard Country or Area Codes for Statistical Use (M49), Unitd Nations Statistics Division",
       x = "Continent",
       y = "Fredom Index Status Distribution") +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_brewer(
    name = "Freedom Index Status",
    labels = c("Free", "Partially Free", "Not Free"),
    palette = "Blues",
    direction = -1) +
  facet_grid(~Year) +
  theme_classic() + 
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.caption = element_text(face = "italic", hjust = 0),
        panel.grid.minor = element_blank())   
plot3
```
\newpage

## Q2.d

### Create new dataset with Rescaled FiW Index and LDC Status
```{r, warning=FALSE}
# Match country name with country code, same step as in (c)
FiW_q4 <- as.matrix(FiW_cty) # Use the dataset with re-scaled FiW Index
code_q4 <- as.data.frame(countrycode(FiW_cty[,1],
                                     origin = 'country.name',
                                     destination = 'un'))
FiW_q4 <- cbind(FiW_q4, code_q4) # FiW Index of each country-year with matched M94 code
colnames(FiW_q4)[28] <- c("M49 Code") # Change column name
FiW_cty[115,28] <- 583 # Assign the country code of Micronesia

# Combine the FiW Index dataset and LDC classification dataset by UN
# Match each row in FiW_cty with information in UNSD dataset based on M94 Code
W_LDC_FiW <- left_join(FiW_q4, UNSD, by = "M49 Code") 
W_LDC_FiW <-W_LDC_FiW %>%
  select(-contains("country"), - contains("Region"),-`M49 Code`) %>%
  select(`Least Developed Countries (LDC)`, everything())
colnames(W_LDC_FiW)[1] <- "LDC" # Rename the LDC status column

# Convert the LDC status column into numeric format
W_LDC_FiW <- W_LDC_FiW %>%
  mutate(`LDC` = ifelse(LDC == "x", 1,0)) # 1 represents LDC country
W_LDC_FiW$LDC[is.na(W_LDC_FiW$LDC)] <- 0 # 0, i.e. NA represents non-LDC country
# Convert all FiW Index Value Column into numeric format
W_LDC_FiW <- W_LDC_FiW %>%
  mutate_at(c(2:27), as.numeric) 
# Subset data based on LDC status
LDC <-  W_LDC_FiW %>% # Least Developing Countries
 filter(LDC == 1)
Non_LDC <-  W_LDC_FiW %>% # Non- Least Developing Countries
 filter(LDC == 0)

# Create the dataset of average FiW Index value by LDC status from 1995 to 2020
q4_AVG <- as.data.frame(colMeans(W_LDC_FiW,na.rm = T)) # Total Average
q4_AVG$LDC <- colMeans(LDC, na.rm = T) # Average of LDC countries
q4_AVG$Non_LDC <- colMeans(Non_LDC, na.rm = T) # Average of Non-LDC countries
colnames(q4_AVG)<- c("Total", "LDC", "Non_LDC") # Format the row names

# Cleaning the Final dataset
q4_AVG <- q4_AVG %>% 
  format(digits = 3) %>% # Format the digits
  slice(-c(1)) %>% # Remove LDC Status row
  mutate(Year = c(1995:2020)) %>% # Create the Year Column
  mutate_at(c(1:4), as.numeric) %>% # Format columns into numeric category
  mutate(Diff = Non_LDC - LDC) # Calculate difference of Average FiW Index by LDC Status
rownames(q4_AVG) <- c(1:26) # Format rownames
```

### Plot the Average FiW Index by LDC Status from 1995 to 2020
```{r}
# Draw the main plot
plot_q4 <- q4_AVG %>%
  ggplot() +
  geom_line(mapping = aes(x=Year, y= `LDC`, # Plot trend line of LDC's average FiW Value
                          color = "LDC"),size = 0.7) +
  geom_point(aes(x = 2020, y = 0.389, # Plot point value of LDC's average FiW in 2020
                 color = "LDC"), size = 2) +
  geom_line(mapping = aes(x=Year, y= `Non_LDC`,# Plot trend line of Non-LDC
                          color = "Non_LDC"), size = 0.7) + 
  geom_point(aes(x = 2020, y = 0.648, # Plot point value of Non-LDC in 2020
                 color = "Non_LDC"), size = 2) + 
  geom_line(mapping = aes(x=Year, y= `Total`,# Plot trend line of All Countries
                          color = "Total"), size = 0.7, linetype = "longdash") + 
  geom_point(aes(x = 2020, y = 0.587, # Plot point value of All Countries in 2020
                 color = "Total"), size = 2) +
  scale_x_continuous(breaks = c(1995,2000,2005,2010,2015,2020),
                     limits = c(1993,2022)) + # Format x  axis
  scale_y_continuous(breaks = c(0.3,0.4,0.5,0.6,0.7),
                     limits = c(0.3,0.7)) + # Format y axis
  labs(title = "Average Freedom Index by countries' development Status",
       subtitle = "Year 1995 to 2020",caption =
  "Source: Freedom House.(2021).Country and Territory Ratings and Statues, 1973-2021.
Standard Country or Area Codes for Statistical Use (M49), Unitd Nations Statistics Division",
    x = "Year",
    y = "Average Value of Re-scaled FiW Index") +
  scale_color_manual(
    name = "Country Category", # Customize legend's name
    labels = c("Least-developed", "Non Least-developed","All"), # Customize labels' name
    values= c("#1B9E77","#D95F02","#7570B3")) +
  theme_bw() +
  theme(plot.title = element_text(size = 14, face = "bold"),
        plot.caption = element_text(face = "italic", hjust = 0),
        panel.grid.minor = element_blank()
  )  
#  Add annotations of key values
plot_q4 +
  annotate(geom = "label",x = 1995, y = 0.372, # label Average FiW of LDC in 1995
  label = "0.383", color = "#1B9E77", fill = NA, fontface = "bold", label.size =NA) +
  annotate(geom = "label", x = 1995, y = 0.604,  # label Average FiW of Non-LDC in 1995
  label = "0.613", color = "#D95F02",fill = NA, fontface = "bold", label.size =NA) +
  annotate(geom = "label", x = 1995, y = 0.55,  # label Average FiW of All in 1995
  label = "0.560", color = "#7570B3",fill =NA,  fontface = "bold", label.size =NA) +
  annotate(geom = "label", x = 2020, y = 0.373, # label Average FiW of LDC in 2020
  label = "0.389", color = "#1B9E77", fill = NA, fontface = "bold", label.size =NA) +
  annotate(geom = "label", x = 2020, y = 0.63, # label Average FiW of Non-LDC in 2020
  label = "0.648", color = "#D95F02",fill = NA, fontface = "bold", label.size =NA) +
  annotate(geom = "label", x = 2020, y = 0.571,  # label Average FiW of All in 2020
  label = "0.587", color = "#7570B3", fill = NA, fontface = "bold", label.size =NA) +
  annotate(geom = "label", x = 2006, y = 0.464, # label highest Average FiW of LDC
  label = "0.452", color = "#1B9E77", fill = NA, fontface = "bold", label.size =NA) +
  annotate(geom = "label", x = 2005, y = 0.699, # label highest Average FiW of Non-LDC
  label = "0.687", color = "#D95F02",fill = NA, fontface = "bold", label.size =NA) +
  annotate(geom = "label", x = 2005, y = 0.641,  # label highest Average FiW of All
  label = "0.630", color = "#7570B3", fill = NA, fontface = "bold", label.size =NA)

# Plot the difference of average FiW values between LDC countries and Non-lDC countries
plot_q4_diff <- q4_AVG %>%
  ggplot() +
  geom_line(aes(x=Year, y= `Diff`,#Plot trend line of Differences of average FiW Value
                color = "Diff"),
            size = 0.7, linetype = "twodash") +
  scale_x_continuous(breaks = c(1995,2000,2005,2010,2015,2020),
                     limits = c(1995,2020)) + # Format x  axis
  scale_y_continuous(breaks = c(0.2,0.25,0.3),
                     limits = c(0.2,0.3)) + # Format y axis
  labs(title = "Difference of Average Freedom Index among
LDC and Non-LDC Countries(Year 1995 to 2020)",caption =
  "Source: Freedom House.(2021).Country and Territory Ratings and Statues, 1973-2021.
Standard Country or Area Codes for Statistical Use (M49), Unitd Nations Statistics Division",
    x = "Year",
    y = "Difference of Average FiW Value") +
  scale_color_manual(name = "Legend",
                     labels = c("Difference"), 
                     values= c("#D73027")) + 
  annotate(geom = "label",
           x = 1995, y = 0.227, # label average FiW Difference in 1995
           label = "0.23", color = "#D73027", fill = NA, 
           fontface = "bold", label.size = NA) +
  annotate(geom = "label", x = 2020, y = 0.266,  # label average FiW Difference in 2020
           label = "0.259", color = "#D73027", fill = NA,
           fontface = "bold", label.size = NA) +
  annotate(geom = "label", x = 2006, y = 0.225,  # label the lowest average FiW Difference
           label = "0.229", color = "#D73027", fill = NA,
           fontface = "bold", label.size = NA) +
  theme_bw() +
  theme(plot.title = element_text(size = 14, face = "bold"),
        plot.caption = element_text(face = "italic", hjust = 0),
        panel.grid.minor = element_blank()
  )
plot_q4_diff
```